### 2013-04-03 writing/article.Rmd
Initial commit

Отношение к высшему образованию: сентимент-анализ данных микроблогов
========================================================
**Гедранович Б.А, Гедранович А.Б**
**********************************

```{r include=FALSE}
require(knitcitations)
require(bibtex)
biblio <- read.bib("ref.bib")
```

Введение
------------------
В работе `r citet(biblio[[1]])`...

На сайте `r citet("http://wikipedia.org")` ...

Сентимент-анализ
------------------

Описание данных
------------------

Результаты
------------------

Заключение
------------------

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

Литература
--------------
```{r results='asis', echo=FALSE}
bibliography()
```